decompr: trade flow decomposition for Global Value Chain analysis

### 2014-12-04 README.Rmd
Abbreviation for WWZ

The Wang-Wei-Zhu decomposition goes a step further by not only revealing the source of the value added,
but also breaking down exports into different categories, based on its usage and final destination.

>>>>

The Wang-Wei-Zhu (henceforth WWZ) decomposition goes a step further by not only revealing the source of the value added,
but also breaking down exports into different categories, based on its usage and final destination.
